\section{Thesis Outline}
\label{intro:thesis outline}

This thesis is divided into four parts, specifically: $(1)$ Background and Introduction, $(2)$ Joint Analyticity of the Upper and Lower Fields, $(3)$ Numerical Results and Scattering, and $(4)$ Concluding Remarks and Future Research. The ``Joint Analyticity of the Upper and Lower Fields" part is contained in Chapters $2$--$4$. In Chapters $2$ and $3$, we discuss our general strategy for establishing analyticity results which are based on a special change of variables and the elliptic theory of Sobolev spaces. The concluding section of these chapters details the mechanics of our HOPS algorithm and provides example profiles where our algorithm is highly accurate and robust. Chapter $4$ combines these results to establish our main theorem (Theorem $4.6.1$) which proves the existence and uniqueness of solutions to a system of partial differential equations with respect to both interfacial and frequency deformations.

The ``Numerical Results and Scattering" part is composed of Chapters $5$ and $6$. In Chapter $5$, we describe the Method of Manufactured Solutions as a tool to demonstrate the accuracy of our HOPS algorithm. Then, in Chapter 6, we define the Reflectivity Map as a way of computing the reflected energy stored by a periodic structure. We simulate a large variety of scattering problems using a range of wavelengths and dielectric constants in both the TE and TM propagation modes. The ``Concluding Remarks" part is given in Chapter $7$ where we discuss several different possibilities for future research. Among these, the most interesting is Section $7.4$ where we analyze the necessary steps to extend our analyticality theorem from two parameters to any finite integer $M>0$.