%\acknowledgments
%\section*{ACKNOWLEDGEMENTS}

\acknowledgments
\label{Sec:Acknowledgments}
% match spacing in thesis.tex
\setstretch{1.3}
I would like to thank my advisor, David Nicholls. David has been my mentor since January 2018 and has done an outstanding job teaching me about the fields of numerical analysis, electromagnetics, and spectral element methods. His skills in computational mathematics (and in programming languages such as Matlab) have been invaluable in completing this thesis. I was lucky to have an extremely supportive advisor and couldn't have asked for a kinder person. I would also like to thank the other members of my thesis committee, including Gerard Awanou, Mimi Dai, Jan Verschelde, and Thomas Royston. I thank them for agreeing to review my thesis and have benefited from their mathematical knowledge and the face-to-face conversations we had at UIC.

I've also been fortunate to work with a lot of instructors and professors at UIC. I would like to thank Rafail Abramov, Jerry Bona, Alexey Cheskidov, Christof Sparber, Ian Tobasco, and Gyorgy Turan for speaking with me inside and outside of office hours. I also want to thank Gerard Awanou for teaching me about the theory and applications of the finite element and finite difference methods, as well as Mimi Dai for helping me improve my intuition for elliptic partial differential equations.  Additionally, I am grateful to Jan Verschelde for mentoring me during my first semester as a graduate assistant for numerical analysis. I enjoyed working as a graduate teaching assistant and would like to thank Martina Bode, Matthew Lee, Jennifer Ross, Andrew Schulman, and John Steenbergen. Because of their constructive feedback, I have become a more experienced math instructor and am significantly more confident in my teaching abilities than when I started four years ago.

As a computational mathematician, I was graciously offered two summer internships through the NSF MSGI program. My first internship was at Argonne National Laboratory where I learned about the fields of tomography, the Radon transform, and inverse problems. I am thankful for the guidance from my mentor, Wendy Dai, and also for the programming help from Matthew Otten. I enjoyed working on parallel programming techniques and am fascinated by the work done on the Beebop supercomputer. My second internship was at the Cold Regions Research and Engineering Laboratory (CRREL) where I worked on two thermodynamic models (FROST and FROSTb) which predict  frost-depth penetration. I would like to thank my mentor Scott Michael Slone for his assistance with the Elmer FEM software and his positive personality which made programming in Fortran more enjoyable. I would also like to thank the organizers of the MSRI Summer School programs for the interesting material presented in the summer schools on water waves, microlocal analysis, and the mathematics of big data.

In the engineering department at UIC, I have developed friendships with many graduate students who enjoy application--oriented mathematics. I fondly remember speaking with Daniel Wen about the relationship between mathematicians and engineers and our weekly badminton sessions. I enjoyed arguing with Dan about everything and wish him the best of luck with his family in California. I also enjoyed speaking with Sam Englender throughout my brief visits to Michigan and with Neelima Borade, Joondo Chang, Jacob Mayle, and Margaret Hoeller in SEO and throughout the different math classes we had together.

My family has always been supportive of me throughout my education. I would like to thank my mother and father for the continued emotional support and for putting up with old conversations about ``calculating zeros of the Riemann zeta function." My twin brother Jeff is also an engineer and is interested in mathematics. I wish him well and hope that his wedding in August goes smoothly. Both of my sisters and their husbands have also been very kind to me and I know that they will do a good job raising a family together. I'd also like to thank Frank Massey, Paul Howard, and all the other math instructors who taught me that math was interesting when I was initially focused on becoming a computer programmer.

% This line is required, but of course replace my initials with yours.
\initials{MSK}
\thispagestyle{pageonbottom}
